\papertitle

### 2017-03-23 article-icmc2017.tex
work

@@

\subsection{In the cables between ports}
The most precise way to set-up dependency-related information would be in 
the cables connecting two ports.

@@

\subsection{In the ports}
\subsection{In the nodes}
\subsection{In the addresses}
No temporal behaviour possible
\subsection{Global behaviour}
No temporal behaviour possible
\subsection{Overall resolution}
Unspecified by default.

Hierarchical: cable, port, node, address, global.

Default global behaviour: glutton.

@@

\begin{figure}
  \begin{subfigure}{0.20\textwidth }    		    		
    \begin{itemize}
      \item $t_0$: $f_1$.
      \item $t_1$: $f_2 \circ f_1$.
      \item $t_2$: $f_2$. 
    \end{itemize}
    \caption{Glutton execution in the order of the fig.~\ref{fig.simple}}
  \end{subfigure}~
  \begin{subfigure}{0.20\textwidth}

    \begin{itemize}
      \item $t_0$: $f_2$.
      \item $t_1$: $f_1 \circ f_2$.
      \item $t_2$: $f_1$. 
    \end{itemize}
    \caption{
    	Glutton execution in the case of fig.~\ref{fig.simple-reversed}}
  \end{subfigure}
  \caption{}
\end{figure}

\section{Evaluation algorithm}
- Split the tick in steps
- Each step, go to the next elements (follow the cables) and find all the nodes that can be currently called.
%We present here the evaluation algorithm that operates at each tick.

%Divide the time in abstract segment according to the activation graph; gives us a set of equations for each variable.
\section{Implementation}
\section{Conclusion}
Additional consideration: see PLOP 2006 article (multi-stream, etc), sample accuracy, etc

Explicit cables: optimization.

Generalization to not only a single variable of time, but any kind of driving parameters
\section{Acknowledgements}
\printbibliography 
\end{document}

>>>>

Arumi presents in~\cite{arumi2006dataflow} the advantages and drawbacks of both approaches.

@@

The most obvious candidates are the cables betweens ports, and the dependency edges between nodes of the dataflow.

The most precise way to set-up dependency-related information would be in 
the cables connecting two ports.

@@

\subsection{Other}
Default behaviours can be encoded either globally, per address, or hierarchically in a timeflow.

However, temporal behaviours cannot be encoded this way.

We choose a default glutton behaviour; however usability studies should be led to determine the most user-friendly default behaviour.

@@

With the OSSIA semantics, this order could change at each run of a score.

\begin{figure}[h]
  \begin{subfigure}{0.20\textwidth }    		    		
    \begin{itemize}
      \item $t_0$: $f_1$.
      \item $t_1$: $f_2 \circ f_1$.
      \item $t_2$: $f_2$. 
    \end{itemize}
    \caption{Glutton execution in the order of the fig.~\ref{fig.simple}}
  \end{subfigure}~
  \begin{subfigure}{0.20\textwidth}

    \begin{itemize}
      \item $t_0$: $f_2$.
      \item $t_1$: $f_1 \circ f_2$.
      \item $t_2$: $f_1$. 
    \end{itemize}
    \caption{
    	Glutton execution in the case of fig.~\ref{fig.simple-reversed}}
  \end{subfigure}
  \caption{Executions with a temporal ordering}
\end{figure}

%\section{Evaluation algorithm}
%- Split the tick in steps
%- Each step, go to the next elements (follow the cables) and find all the nodes that can be currently called.
%We present here the evaluation algorithm that operates at each tick.

%Divide the time in abstract segment according to the activation graph; gives us a set of equations for each variable.
%\section{Implementation}
\section{Conclusion}
%Additional consideration: see PLOP 2006 article (multi-stream, etc), sample accuracy, etc

%Explicit cables: optimization.

%Generalization to not only a single variable of time, but any kind of driving parameters
\section{Acknowledgements}
Redacted.
\printbibliography 
\end{document}
